Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-24 doc/manuscript/ESSDmanuscript.tex
worked on Table 2

 & (covariates) & Other Properties & direct mapping & no\\

@@

 & allometry & Comments from Data Provider & link to biomass allometry source & \\

@@

 & data.location.within.source &  & confirm that data weren't digitized, facilitate finding data in original publication & yes\\

@@

History & (need to detail this) & 1996 Source/Sink Categories, 2006 Source/Sink Categories & used to determine distmrs.type & (yes)\\
 & (need to detail this) & Abatement/Control technologies & generate list management events & no\\

>>>>

 & depth, covariate\_1, cov\_1.value, covariate\_2, cov\_2.value & Other Properties & direct mapping & no\\

@@

 & allometry\_1, allometry\_2 & Comments from Data Provider & link to biomass allometry source, when provided & no\\

@@

 & data.location.within.source & - & confirm that data weren't digitized, facilitate finding data in original publication & yes\\

@@

History & date, hist.cat, hist.type & 1996 Source/Sink Categories, 2006 Source/Sink Categories, Abatement/Control technologies & used to determine distmrs.type for Source/Sink Categories, generate list of events for Abatement/Control technologies & (yes)\\
